
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% IIT Sample THESIS File,   Version 3, Updated by Babak Hamidian on 11/18/2003
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% File: sample3.tex                                   %
% IIT Sample LaTeX File                               %
% by Ozlem Kalinli on 05/30/2003                      %
% Revised by Babak Hamidian on 11/18/2003             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                     %
% This is a sample thesis document created using      %
% iitthesis.cls style file. The PDF output is also    %
% available for your reference. In this file, it has  %
% been illustrated how to make table of contents,     %
% list of tables, list of figures, list of symbols,   %
% bibliography, equations, enumerations, etc.         %
% You can find detailed instructions                  %
% for using the style file in Help.doc,               %
% TableHelp.doc, FigureHelp.doc, and                  %
% Bibliography.doc files.                             %
%                                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Note: The texts that are used in this sample3.tex   %
% file are irrelevant. They are just used to show     %
% you the style created by iitthesis style file.      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{iitthesis}


% Document Options:
%
% Note if you want to save paper when printing drafts,
% replace the above line by
%
%   \documentclass[draft]{iitthesis}
%
% See Help file for more about options.
\usepackage[dvips]{graphicx}    % This package is used for Figures
\usepackage{rotating}           % This package is used for landscape mode.
\usepackage{epsfig}
\usepackage{float}
\usepackage{subfigure}          % These two packages, epsfig and subfigure, are used for creating subplots.
% Packages are explained in the Help document.

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}
\usepackage{hyperref}
\usepackage{epigraph}
\usepackage{cite}

% *** ALGORITHM ***
%\usepackage{algorithm}
%\usepackage{algpseudocode}
\usepackage[ruled, linesnumbered]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage{comment}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{xspace}


% *** To balance reference page ***
\usepackage[keeplastbox]{flushend}

% *** Draw diagrams ***
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}

% *** Fancy Table ***
\usepackage{multirow}
\usepackage{tablefootnote}

% *** Highlight changes ***
\usepackage{color, soul}

\newcommand{\paragraphb}[1]{\vspace{0.03in}\noindent{\bf #1} }
\newcommand{\paragraphe}[1]{\vspace{0.03in}\noindent{\em #1} }
\newcommand{\paragraphbe}[1]{\vspace{0.03in}\noindent{\bf \em #1} }

% System name for MAGIC
\newcommand{\sysname}{MAGIC\xspace}

\begin{document}

%%% Declarations for Title Page %%%
\title{A Scalable Simulation and Modeling Framework for Evaluation of
Software-Defined Networking Design and Security Applications
}
\author{Jiaqi Yan}
\degree{Doctor of Philosophy}
\dept{Computer Science}
\date{October 2019}
\copyrightnoticetrue      % crate copyright page or not
%\coadvisortrue           % add co-advisor. activate it by removing % symbol to add co-advisor
\maketitle                % create title and copyright pages


\prelimpages         % Settings of preliminary pages are done with \prelimpages command


%%%  Acknowledgement %%%
%\begin{acknowledgement}     % acknowledgement environment, this is optional
%\par  This dissertation could not have been written without Dr. X
%who not only served as my supervisor but also encouraged and
%challenged me throughout my academic program. He and the other
%faculty members, Dr. Y and Dr. Z, guided me through the
%dissertation process, never accepting less than my best efforts. I
%thank them all.\\ \\ (Don't copy this sample text. Write your own
%acknowledgement.)
%\end{acknowledgement}


% Table of Contents
\tableofcontents
\clearpage

% List of Tables
\listoftables

\clearpage

%List of Figures
\listoffigures

\clearpage

%List of Symbols(optional)

%\listofsymbols
%\SymbolDefinition{$\beta$}{probability of non-detecting bad data}
%\SymbolDefinition{$\delta$}{Transition Coefficient Constant for the Design of Linear-Phase FIR Filters}
%\SymbolDefinition{$\zeta$}{Reflection Coefficient Parameter}

\clearpage



%%% Abstract %%%
\begin{abstract}           % abstract environment, this is optional
    \par
    The world today is densely connected by many large-scale computer networks, supporting military applications,
    social communications, power grid facilities, cloud services, and other critical infrastructures.
    However, a gap has grown between the complexity of the system and the increasing need for security and resilience.
    We believe this gap is now reaching a tipping point, resulting in a dramatic change in the way
    that networks and applications are architected, developed, monitored, and protected.
    This trend calls for a scalable and high-fidelity network testing and evaluation platform to
    facilitate the transformation from in-house research ideas to real-world working solutions.

    With this objective, we investigate means to design and build a scalable and high-fidelity network testbed
    using container-based emulation and parallel simulation; and our study focuses on the emerging software-defined networking (SDN) technology.
    Existing simulation and emulation platforms facilitate the adoption of the SDN-based network architecture
    and applications to production systems.
    However, the performance of those platforms is highly dependent on the underlying physical hardware resources.
    Insufficient resources would lead to undesired results, such as low experimental fidelity or slow execution speed,
    especially with large-scale network settings.

    To improve the testbed fidelity, we first develop a lightweight virtual time system for Linux container
    and integrate the system into a widely-used SDN emulator.
    A key issue with an ordinary Linux-container based emulator is that it uses the system clock across all
    the containers even if a container is not being scheduled to run, which leads to the issue of both performance and temporal fidelity,
    especially with high workloads.
    We investigate virtual time approaches by precisely scaling the time of interactions between containers and physical devices.
    Our evaluation results indicate a definite improvement in fidelity and scalability,
    and the virtual time system enables efficient clock synchronization algorithms between simulation and emulation systems.

    To improve the testbed scalability, we investigate how the centralized paradigm of SDN-based networks
    can be utilized to reduce the simulation workload.
    We explore a model abstraction technique that effectively transforms the network devices in
    an SDN-based network to one virtualized switch model.
    While significantly reducing the model execution time and enabling the real-time simulation capability,
    our abstracted model also preserves the end-to-end forwarding behavior of the original network.

    With enhanced fidelity and scalability, it is realistic to utilize our network testbed to
    perform security evaluation of various SDN applications, particular in the context of smart grid's communication network.
    We notice that both the communication network and power grid are complex systems that generate and process a huge amount of data.
    The logically-centralized SDN control plan, on the one hand,
    has to process the inquiries from the networks (e.g., critical control and potentially big data traffic),
    and on the other hand, enables many efficient security solutions, such as intrusion detection, mitigation, and prevention.
    Recently, deep neural networks achieve state-of-the-art results across a range of hard problem spaces,
    such as image classification and natural language processing.
    We want to study how to utilize the big data and deep learning to secure communication networks and host entities.

    Our first focus is to use deep-learning based approach for network intrusion detection.
    The initial approach targets on a general communication network and datasets.
    We have performed the feasibility study of off-line deep-learning based intrusion detection
    by constructing the detection engine with multiple advanced deep learning models.
    In the future, we will investigate SDN specific solutions and apply the solutions in the domain of modern power systems.

    Host-based malware detection and classification is another necessary mechanism to secure computer system.
    This becomes particular critical for the SDN controller host that is vulnerable to single point failure.
    Existing machine learning-based malware classification methods rely on handcrafted features extracted from raw binary files or disassembled code.
    The diversity of such features created has made it hard to build generic malware classification systems that
    work effectively across different operational environments.
    To strike a balance between generality and performance,
    we explore new machine learning techniques to classify malware programs represented as their control flow graphs.
    The resultant innovative system uses deep graph convolutional neural network to
    embed structural information inherent in control flow graphs for effective yet efficient malware classification.

    %Realistic and scalable testing platforms for computer network system are critical for multiple application domains.
    %Network operators heavily relies on them to evaluate the functionality and the performance of their communication infrastructures and protocols.
    %Replaying the cyber-attacks happened in real world and, more importantly, practicing, as well as evaluating, the countermeasures become 
    %enormously difficult if without a virtually simulated or emulated testbed.
    %Meanwhile, the network today in many domains and settings, are evolving toward the software-defined networking (SDN) paradigm.
    %Multiple SDN simulation and emulation platforms have help expedite the adoption of many emerging SDN-based applications to production systems.
    %However, all of those virtual simulation or emulation testbeds are highly coupled with the underlying available physical hardware resources.
    %As the result, their correctness will be corrupted, their scalability limited, and their fidelity compromised,
    %especially exposed under the common large-scale network settings.
    %Under the centre theme of securing SDN-enabled large-scale network using high-fidelity and scalable testing system, our research work has three streams.

    %Linux-container-based network emulation (LCNE) combines many desired features of software simulators and physical testbeds.
    %Therefore, first we ask not what LCNE can do for computer network -- ask what we can do for LCNE.
    %Specifically, we address one of the key issues -- an ordinary Linux-container based SDN emulator
    %uses the system clock across all the containers even if a container is not being scheduled to run.
    %This leads to the issue of both performance and temporal fidelity, especially with high workloads.
    %Virtual time sheds the light on this issue by precisely scaling the time of interactions between containers and physical devices.
    %We develope a lightweight Linux-container-based virtual time system and integrate it to Mininet.
    %Except for enhancing Minint's fidelity and scalability,
    %our virtual time system is also an alternative for synchronizing clocks in hybrid simulation and emulation.

    %Second, we ask not what simulation will do for SDN-enabled network,
    %but ask what the centralized paradigm can do for the methodology that simulates itself.
    %Following this idea, we present a model abstraction technique that effectively transforms
    %the network devices in an SDN-based network to one virtualized switch model.
    %While significantly reducing the model execution time and enabling the real-time simulation capability,
    %our abstracted model also preserves the end-to-end forwarding behavior of the original network.

    %Recently, deep neural networks achieve state-of-the-art results across a range of hard problem spaces,
    %such as image classification and natural language processing,
    %Therefore, we ask what together simulation/emulation testing system and deep learning technology can do for network security.
    %Our answer is anomaly detection based network intrusion detection systems (NIDS),
    %the essential network-architecture-agnostic security building-blocks.
    %We study the feasibility of off-line deep learning based NIDS by constructing the detection engine with multiple advanced deep learning models.

\end{abstract}


\textpages     % Settings of text-pages are done with \textpages command

% Chapters are created with \Chapter{title} command
\Chapter{Introduction}
\input{intro}

\Chapter{Overview of Related Works}
\label{Cpt:RelatedWorks}
\input{VirtualTime/related_works}
\input{OneBigSwitch/related_works}
\input{CompareDL/related_works}
\input{Magic/related_works}

\Chapter{Virtual Time System}
\label{Cpt:VTS}
\input{VirtualTime/motivation}
\input{VirtualTime/design}
\input{VirtualTime/implementation}
\input{VirtualTime/evaluation}
\input{VirtualTime/case_study}
\input{VirtualTime/conclusion}
\clearpage

\Chapter{One Big Switch}
\label{Cpt:OBS}
\input{OneBigSwitch/motivation}
\input{OneBigSwitch/example}
\input{OneBigSwitch/design}
\input{OneBigSwitch/evaluation}
\input{OneBigSwitch/conclusion}
\clearpage

\Chapter{Deep Learning for Network Intrusion Detection}
\label{Chp:DLNID}
\input{CompareDL/background}
\input{CompareDL/datasets}
\input{CompareDL/architectures}
\input{CompareDL/evaluation}
\input{CompareDL/conclusion}
\clearpage

\Chapter{Deep Learning for Malware Classification}
\label{Cpt:DLMC}
\input{Magic/system_design}
\input{Magic/dgcnn}
\input{Magic/implementation}
\input{Magic/experiments}
\input{Magic/conclusion}
\clearpage

\Chapter{Conclusion}
\label{Cpt:Conclusion}
\input{conclusion}

%
% APPENDIX
%
% Do the settings of appendices with \appendix command
\appendix

% Then create each appendix using
% \Appendix{title_of_appendix} command
%
% BIBLIOGRAPHY
%
% you have two options: 1) create bibliography manually,
% 2) create bibliography automatically. See BibliographyHelp.pdf file for details.
\bibliographystyle{plain}
\bibliography{mybib}

\end{document}  % end of document
